R for Clinical Study Reports and Submission

### 2021-11-17 tlf-ae-summary.Rmd
Update a few wording
Co-authored-by: yilong zhang <elong0527@gmail.com>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we need the number of participants were included in each safety analysis in Section 12.2, Adverse Events (AEs).

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
we summarize number of participants that were included in each safety analysis in Section 12.2, Adverse Events (AEs).
